Structured Versus Decorated Cospans

### 2021-03-29 cospans_new.tex
a few small improvements to Kenny's new (3/28/2021) version

% Structured versus decorated cospans
% John Baez, Kenny Courser and Christina Vasilakopoulou
% in LaTeX
% 2021/3/15 - attempt at new version

@@

\begin{proof}[Proof of \cref{thm:decorated_cospans_1}] We apply \cref{lem:shulman} to the Beck-Chevalley monoidal bifibration $U_1 \colon (\A/U) \to \A$ which we now define. Let $(\A/U)$ be the comma category in which:
\begin{enumerate}
\item{an object is a triple $(a,x,a \xrightarrow{i} U(x))$, and}
\item{a morphism from $(a,x,a \xrightarrow{i} U(x))$ to $(a',x',a' \xrightarrow{i'} U(x'))$ is a pair of morphisms $f \colon a \to a'$ and $\alpha \colon x \to x'$ such that the following square commutes:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$a'$};
\node (C) at (0,-1) {$U(x)$};
\node (D) at (1,-1) {$U(x')$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$f$} (B)
(A) edge node[left]{$i$} (C)
(B) edge node[right]{$i'$} (D)
(C) edge node[above]{$U(\alpha)$} (D);
\end{tikzpicture}
\]}
\end{enumerate}
The functor $U_1$ is defined on objects by $U_1(a,x,a \xrightarrow{i} U(x))=a$ and on morphisms by $U_1(f,\alpha)=f$. We have a monoidal structure on the comma category $(\A/U)$ where the tensor product of two objects $(a_1,x_1,a_1 \xrightarrow{i_1} U(x_1))$ and $(a_2,x_2,a_2 \xrightarrow{i_2} U(x_2))$ is given by $$(a_1,x_1,a_1 \xrightarrow{i_1} U(x_1)) \otimes (a_2,x_2,a_2 \xrightarrow{i_2} U(x_2)) = (a_1+a_2,x_1+x_2,a_1+a_2 \xrightarrow{i_1+i_2} U(x_1+x_2))$$making use of the natural isomorphism $U(x_1)+U(x_2) \cong U(x_1+x_2)$ which we omit in the above definition. The monoidal unit is given by $(0_\A,0_\X,0_\A \to U(0_\X))$. It is easy to see that the functor $U_1$ can be made into a strict monoidal functor using this tensor product.

>>>>

% Structured versus decorated cospans
% John Baez, Kenny Courser and Christina Vasilakopoulou
% in LaTeX
% 2021/3/29 - Kenny's changes

@@

\begin{proof}[Proof of \cref{thm:decorated_cospans_1}] We apply \cref{lem:shulman} to the Beck-Chevalley monoidal bifibration $U_1 \colon (\A/U) \to \A$ which we now define. Let $(\A/U)$ be the comma category in which:
\begin{enumerate}
\item{an object is a triple $(a,x,a \xrightarrow{i} U(x))$, and}
\item{a morphism from $(a,x,a \xrightarrow{i} U(x))$ to $(a',x',a' \xrightarrow{i'} U(x'))$ is a pair of morphisms $f \colon a \to a'$ and $\alpha \colon x \to x'$ such that the following square commutes:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$a'$};
\node (C) at (0,-1) {$U(x)$};
\node (D) at (1,-1) {$U(x')$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$f$} (B)
(A) edge node[left]{$i$} (C)
(B) edge node[right]{$i'$} (D)
(C) edge node[above]{$U(\alpha)$} (D);
\end{tikzpicture}
\]}
\end{enumerate}
The functor $U_1$ is defined on objects by $U_1(a,x,a \xrightarrow{i} U(x))=a$ and on morphisms by $U_1(f,\alpha)=f$. We have a monoidal structure on the comma category $(\A/U)$ where the tensor product of two objects $(a_1,x_1,a_1 \xrightarrow{i_1} U(x_1))$ and $(a_2,x_2,a_2 \xrightarrow{i_2} U(x_2))$ is given by
 $$(a_1,x_1,a_1 \xrightarrow{i_1} U(x_1)) \otimes (a_2,x_2,a_2 \xrightarrow{i_2} U(x_2)) = (a_1+a_2,x_1+x_2,a_1+a_2 \xrightarrow{i_1+i_2} U(x_1+x_2))$$
where the natural isomorphism $U(x_1)+U(x_2) \cong U(x_1+x_2)$ is implicit
 in the above composite, for reasons of space. The monoidal unit is given by $(0_\A,0_\X,0_\A \to U(0_\X))$. It is easy to see that the functor $U_1$ can be made into a strict monoidal functor using this tensor product.
